Corpus

### 2021-08-11 analysis/corpus.Rmd
Update Kaggle
Remove axis label

eval_call_sites_hist(PKG_C, CRAN_C, "CRAN packages")
ggsave(path(PLOT_DIR, "pkgs-eval-callsites-hist.pdf"))
eval_call_sites_hist(KAGGLE, KAGGLE_ALL, "KAGGLE programs")
ggsave(path(PLOT_DIR, "kaggle-eval-callsites-hist.pdf"))
```

@@

eval_plot_df %>% 
#  filter(evals > 0, evals_hit > 0) %>%
  mutate(
    # size=cut(package_r_code, size_breaks, size_labels, include.lowest=T),
    label=ifelse(evals %in% tail(sort(evals),3), package, NA)
  ) %>%
  ggplot(aes(x=evals, y=evals_hit, size=package_r_code, label=label)) + 
    geom_jitter(alpha=0.3) +
    geom_text(nudge_y = .25, check_overlap = TRUE, size=4) +
    scale_x_continuous(
      trans="log10",
      breaks=function(x) {
        f <- scales::breaks_log()
        sort(c(f(x), max(eval_plot_df$evals)))
      },
      labels=scales::comma_format(accuracy = 1)
    ) +
    scale_y_continuous(
      trans="pseudo_log",
      breaks=function(x) {
        f <- scales::breaks_log()
        sort(c(0, 1, f(c(1, x[2])), max(eval_plot_df$evals_hit)))
      },
      labels=scales::comma_format(accuracy = 1)
    ) +
    scale_size_binned(
      range=c(1,10),
      breaks = size_breaks,
      labels=scales::comma_format(accuracy = 1)
    ) +
#    geom_smooth(method = "lm", se = FALSE, show.legend = FALSE, linetype="dashed", color="red", size=0.2) +
    labs(x="Eval call sites (log)", y="Traced eval call sites (log)", size="Package R code size") +
    theme(
      text = element_text(size=17),
      legend.position = c(0.2, 0.75)
    )
ggsave(path(PLOT_DIR, "traced-eval-callsites.pdf"))
```

>>>>

eval_call_sites_hist(PKG_C, CRAN_C, "")
ggsave(path(PLOT_DIR, "pkgs-eval-callsites-hist.pdf"))

# eval_call_sites_hist(KAGGLE, KAGGLE_ALL, "KAGGLE programs")
# ggsave(path(PLOT_DIR, "kaggle-eval-callsites-hist.pdf"))
```

@@

eval_plot_df %>% 
#  filter(evals > 0, evals_hit > 0) %>%
  mutate(
    # size=cut(package_r_code, size_breaks, size_labels, include.lowest=T),
    label=ifelse(evals %in% tail(sort(evals),3), package, NA)
  ) %>%
  ggplot(aes(x=evals, y=evals_hit, size=package_r_code, label=label)) + 
    geom_jitter(alpha=0.3) +
    geom_text(nudge_y = .25, check_overlap = TRUE, size=4) +
    scale_x_continuous(
      trans="log10",
      breaks=function(x) {
        f <- scales::breaks_log()
        sort(c(f(x), max(eval_plot_df$evals)))
      },
      labels=scales::comma_format(accuracy = 1)
    ) +
    scale_y_continuous(
      trans="pseudo_log",
      breaks=function(x) {
        f <- scales::breaks_log()
        sort(c(0, 1, f(c(1, x[2])), max(eval_plot_df$evals_hit)))
      },
      labels=scales::comma_format(accuracy = 1)
    ) +
    scale_size_binned(
      range=c(1,10),
      breaks = size_breaks,
      labels=scales::comma_format(accuracy = 1)
    ) +
    labs(x="Eval call sites (log)", y="Traced eval call sites (log)", size="Package R code size") +
    theme(
      text = element_text(size=17),
      legend.position = c(0.2, 0.75)
    )
ggsave(path(PLOT_DIR, "traced-eval-callsites.pdf"))
```

## Kaggle extra

The following should be somewhere else

```{r}
kaggle_log <- read_csv(KAGGLE_TRACE_LOG_FILE)
```

```{r}
overview_table(
  r("Kaggle failed scripts", filter(kaggle_log, Exitval != 0))
)
```
